Discriminating the Influence of Correlated Factors \\from Multivariate Observations: the Back-to-Back Regression

### 2020-05-20 paper/response.tex

Reviewers' comments:

Reviewer #1: The authors introduce a novel machine learning approach for the
    prediction of word length and word frequency in MEG time series data. The
    authors begin with an introduction to the problem, their solution, and a
    simulation demonstrating their approach is effective relative to other methods
    focused on the same problem. They demonstrate their approach using a real-world
    example. In short, I have relatively few remarks on their execution, which is
    satisfactory for my tastes. Overall, I think that many researchers in
    neuroimaging will find this technique useful.

    There is one major limitation for the broader application of this approach and
    that's demonstrating its effectiveness in fMRI data. The majority of
    neuroimaging studies are done using fMRI (and I do not say this to discount the
    other valuable tools of EEG, MEG, NIRS, etc.). To get other neuroscientists to
    grab onto this approach, I recommend the authors perform another analysis using
    fMRI data. My suggestion for the authors would be to use data from the Human
    Connectome Project (http://www.humanconnectomeproject.org/). The outcome
    variable used with this approach is not important as so much the demonstration
    that their technique is effective for fMRI data. Without including fMRI data,
    the approach comes off as useful but speculative for fMRI data, which
    drastically limits its impact potential.

We thank Reviewer #1 for this remark. We now applied the same set of analyses to
fMRI recordings of 100 subjects performing a reading experiment similar to the
MEG study described in the paper. We kept the exact same methods and parameters, and
used the fmriprep package to perform the preprocessing, so as to minimize the
risk of p-hacking.

Overall, the results consistently show that B2B compares favorably to other methods.
Furthermore, these novel analyses complements the temporal results obtained with MEG in
that the effects of Word Length are predominantly observed over the early visual
cortices, and the Word Frequency are predominantly observed over the
fronto-temporal areas.

# Reviewer 2

First, the authors justify their approach of using backward modeling by the
    ability to estimate common noise sources. However, this would also be possible
    using multivariate forward modeling. For that reason, I'm wondering how
    multivariate forward modeling would fare under these circumstances. I would find
    it highly informative to include a (similarly cross-validated) multivariate GLM
    to the analyses and results.

We thank Reviewer 2 for this remark. The multivariate GLM / MANOVA is indeed
a relevant analysis. We now indicate in supplementary analyses:

Following the recommendations of one of our reviewers, we also implemented a
multivariate variant of the forward model, i.e. a MANOVA, using the statsmodels
implementation \citep{seabold2010statsmodels}. MANOVA is primarily used as a
inferential statistics, and does not trivially convert to a predicting method.
Consequently, we did not find a way to compare MANOVA against B2B with the
$\Delta R$ evaluation. However, the effects of MANOVA comes with its own effect
size statistics: the Wilk's Lambda. For each searchlight, we thus use the $F-values$ of the
Wilk's Lambda statistics as proxy for $\hat S$ and feeds it to a second-level
Wilcoxon tests across subjects, like we did for the other models.

The results show that all factors, including the Dummy variable, are
systematically above chance level in all recorded brain regions \ref{fig:fmri_supp}. This result
can be explained by the large dimensionality of $Y$. Indeed, limiting the
searchlight to a 1mm radius did not lead to these spurious effects but provided
results similar to the Forward model.

Nonetheless, MANOVA does appear to capture some plausible effects. Indeed, the
$F-values$ obtained for both Word Length and Word Frequency were weakly but
significantly higher than those obtained with the Dummy variable in the
occipital and temporal brain areas \ref{fig:fmri_supp}.

Overall, this suggests that MANOVA (1) can lead to positively biased estimates of
$\hat S$ (2) appears weaker than B2B in terms of second-level analysis across
subjects (3) misses the effect of Word Function detected with the Forward model,
and (4) does not trivially translate into a prediction tool. Together these
elements thus suggest that MANOVA is less suitable to the present objective than
B2B.

> Likewise, while I applaud the authors efforts in conducting these analyses,
    I am wondering whether the impact of this method could not be made even
    stronger by adding more experimental findings. Are there any other openly
    available datasets that could be used to demonstrate the ability to
    disentangle known factors?

As indicated to Reviewer 1, we now successfully apply the same analyses to the fMRI
recordings of 100 subjects reading word sequences.

Other comments:

- Rather than using the feature importance delta_R, is it possible to just
    report the parameter estimate E_hat at each time point? What would be the
    downside of this?

It is possible to report E_hat (now relabelled S_hat). We now added a Supplementary Figure
to that effect. Note, however, that E_hat statistics are not in the same unit as the forward H_hat
coefficients (a.k.a betas values in GLM). Consequently, it is not straightforward to
compare these two metrics directly. As a proxy, we thus report their respective
second-level p-values across subjects. This figure shows show that B2B S_hat
coefficients compare favorably to the Forward H_hat coefficient and the MANOVA coefficients.

- The authors describe their method as unbiased but then introduce two
    regularization parameters, which will bias the estimated coefficients towards
    zero. While the statement "B2B leads to unbiased (i.e. zeros-centered) scalar
    coefficients for non-causal features" is correct for the mean of those
    coefficients, the variance will also be biased. I think these are important
    criteria to consider.

We agree with this remark. We now clarify the meaning and implication of the bias.

Note that $\S hat$ is unbiased, in the sense that it is centered around zero when there is no
effect, only if the second regression $H$ is not regularized. Second-level
statistics testing whether $\S hat$ is superior to 0 are thus only valid if $H$
is not regularized.

- The results of backward regression are not shown in Figure 4, but it would be
    nice to see those results. Is there a possibility to add them to Figure 4 in a
    separate panel?

We now added the decoding performance to a supplementary figure.

- I think the authors could better explain the dimensions of the data (dy
    referring to the number of measurement channels, and dx to the number of
    independent variables). Perhaps the authors could add this nomenclature to their
    graphical illustration? Likewise, for the regression of Y onto X, it is unclear
    if this is a mass-univariate regression or a multivariate regression (i.e.
    taking the error covariance between Ys into account or not). This might be
    obvious to them, but is not necessarily obvious to the reader.

We corrected the text to clarify this issue. However, we did not find an elegant way to
modify the figures.

- I find the choice of the letter E for one of the causal factors unfortunate
    since it is typically reserved for the true error component of a multivariate
    model. Likewise, the choice of N is unfortunate since the letter n has multiple
    meanings in the text: one particular instance of n, or the number of samples.
    This is a very minor comment though.

We now changed $E$ into $S$ for Selection matrix. We also changed the number of
samples into $m$, and keep $N$ as the Noise matrix. Thank you for these suggestions

- Typo line 28: "were" should read "where"?
Corrected.

- Line 181: do the authors refer to the Wilcoxon signed-rank test?
Yes, corrected

### 2020-05-20 paper/appendix.tex
up

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\textwidth,
                     trim=0cm 0cm 0cm 0cm,
                     clip=True]{figures/fmri_decod.pdf}
    \includegraphics[width=0.7\textwidth,
                     trim=0cm 0cm 0cm 0cm,
                     clip=True]{figures/fmri_betas.pdf}

    \label{fig:fmri_supp}
  \end{center}
  \caption{Top. P-values across subjects derived from a Backward decoding of
  each feature (columns). Bottom. P-values across subjects derived from
  the $\beta$ coefficients of a Forward Model and the $\hat S$ of an unbiased
  B2B (i.e. B2B where $H$ is not regularized). Each cell displays the left
  hemisphere view laterally (top) or ventrally (bottom)}
\end{figure}

>>>>

\subsection{Supplementary comparison of models' coefficients}

Following the recommendations of one of our reviewers, we also implemented a
multivariate variant of the forward model, i.e. a MANOVA, using the statsmodels
implementation \citep{seabold2010statsmodels}. MANOVA is primarily used as a
inferential statistics, and does not trivially convert to a predicting method.
Consequently, we did not find a way to compare MANOVA against B2B with the
$\Delta R$ evaluation. However, the effects of MANOVA comes with its own effect
size statistics: the Wilk's Lambda. For each searchlight, we thus use the $F-values$ of the
Wilk's Lambda statistics as proxy for $\hat S$ and feeds it to a second-level
Wilcoxon signed-rank tests across subjects, like we did for the other models.

The results show that all factors, including the Dummy variable, are
systematically above chance level in all recorded brain regions \ref{fig:fmri_supp}. This result
can be explained by the large dimensionality of $Y$. Indeed, limiting the
searchlight to a 1mm radius did not lead to these spurious effects but provided
results similar to the Forward model.

Nonetheless, MANOVA does appear to capture some plausible effects. Indeed, the
$F-values$ obtained for both Word Length and Word Frequency were weakly but
significantly higher than those obtained with the Dummy variable in the
occipital and temporal brain areas \ref{fig:fmri_supp}.

Overall, this suggests that MANOVA (1) can lead to positively biased estimates of
$\hat S$ (2) appears weaker than B2B in terms of second-level analysis across
subjects (3) misses the effect of Word Function detected with the Forward model,
and (4) does not trivially translate into a prediction tool. Together these
elements thus suggest that MANOVA is less suitable to the present objective than
B2B.

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\textwidth,
                     trim=0cm 0cm 0cm 0cm,
                     clip=True]{figures/fmri_controls.pdf}

    \label{fig:fmri_supp}
  \end{center}
  \caption{Top rows. Pearson $R$ correlation obtained for a Backward decoding model and
  a Forward encoding model trained with one factor at a time. These models can
  not take into account the factor covariance, and thus lead to spurious effects
  (e.g. visual cortex effect for the dummy variable). Bottom rows. Second-
  level p-values across subjects for a Forward, a B2B and a Manova trained with
  all factors. The B2B achieves better p-values, without leading to spurious effects for
  the Dummy variable. The Manova leads to biased estimates due to its inability
  to deal with overfitting. The last row shows where the Manova F-values of each factor differs
  significantly from the F-values of the Dummy variable.}
\end{figure}

### 2020-05-20 paper/fmri_exps.tex
up

Each model was implemented for each subject and each time sample independently. Pairwise comparison between models were performed using a two-sided Wilcoxon test across subjects (m=90) using the average $\Delta R$ across time. Corresponding effect sizes are shown in Figure~\ref{fig:meg_results}, and p-values are reported below.

@@

      \label{fig:fmri_delta_r}
  \end{center}
  \caption{Top. Multiple models (rows) are compared on their ability to
  reliably predict out-of-sample fMRI signals evoked by words by quantifying
  the improvement of correlation coefficient $\Delta R$ for each of the four
  features (columns). Each cell displays the left hemisphere view laterally
  (top) or ventrally (bottom). Bottom left. Region
  of Interest (ROI), defined by the cortex vertices that were reliably
  predicted for by the gold standard Forward Model using all features and
  thresholded with a Wilcoxon at $p<0.001$ (uncorrected) across subjects. Bottom
  Right. Average $\Delta R$ within the ROI for each subject
  (dot); top horizontal lines indicate when B2B significantly outperforms
  other methods across subjects.}
\end{figure}

@@

On the contrary, the $\beta$
coefficients of the Forward model reveals the expected spatial specificity of
Word Length and Word Frequency, peaking the visual and temporal cortices
respectively. However such Forward coefficients may be variable across
subjects, and could thus underestimate the significance of each factor at each
vertex, as evaluated with a Wilcoxon tests across subjects. In principle, such
inter-subject variability could be less impactful with
multivariate observations methods such as CCA and PLS \citep{bilenko2016pyrcca,
king2018encoding}, but they fail to provide a single and interpretable coefficient
for each feature at each vertex.

In contrast, the $\hat S$ of an unbiased B2B (i.e. a B2B where $H$ is not
regularized) reaches higher levels of significance at each vertex
than the Forward $\beta$ \ref{fig:fmri_supp}. (Note that a direct
comparison between the Forward coefficients $\beta$ and those of B2B ($\hat S$)
is not feasible, as these two do not have the same units.)

To fairly compare the Forward, CCA, PLS and B2B methods on a common and robust
evaluation metric we compare them on their ability to improve $Y$
predictions of out-of-sample data when one factor is introduced into the model.
This analysis leads to a $\Delta R$ as described in Algorithm
\ref{algorithm:b2b_fi}). As expected, the Forward, CCA, PLS
and B2B method predicted that the Dummy Variable does not improve the $Y$
prediction. This confirms that these methods accurately rule out the known
non-causal factor.

>>>>

Each model was implemented for each subject and each time sample independently.
Pairwise comparison between models were performed using a two-sided Wilcoxon
signed-rank test across subjects (m=90) using the average $\Delta R$ across time.
Corresponding effect sizes are shown in Figure~\ref{fig:meg_results}, and
p-values are reported below.

@@

      \label{fig:fmri_delta_r}
  \end{center}
  \caption{Top. Multiple models (rows) are compared on their ability to
  reliably predict out-of-sample fMRI signals evoked by words by quantifying
  the improvement of correlation coefficient $\Delta R$ for each of the four
  features (columns). Each cell displays the left hemisphere view laterally
  (top) or ventrally (bottom). Bottom left. Region
  of Interest (ROI), defined by the cortex vertices that were reliably
  predicted for by the gold standard Forward Model using all features and
  thresholded with a Wilcoxon signed-rank test at $p<0.001$ (uncorrected) across subjects. Bottom
  Right. Average $\Delta R$ within the ROI for each subject
  (dot); top horizontal lines indicate when B2B significantly outperforms
  other methods across subjects.}
\end{figure}

@@

On the contrary, the $H$
coefficients of the Forward model reveals the expected spatial specificity of
Word Length and Word Frequency, peaking the visual and temporal cortices
respectively. However such Forward coefficients may be variable across
subjects, and could thus underestimate the significance of each factor at each
vertex, as evaluated with a  signed-rank tests across subjects. In principle, such
inter-subject variability could be less impactful with
multivariate observations methods such as CCA and PLS \citep{bilenko2016pyrcca,
king2018encoding}, but they fail to provide a single and interpretable coefficient
for each feature at each vertex.

In contrast, the $\hat S$ of an unbiased B2B (i.e. a B2B where $H$ is not
regularized) reaches higher levels of significance at each vertex
than the Forward $H$ \ref{fig:fmri_supp}. (Note that a direct
comparison between the Forward coefficients $H$ and those of B2B ($\hat S$)
is not feasible, as these two do not have the same units.)

To fairly compare the Forward, CCA, PLS and B2B methods on a common and robust
evaluation metric, robust to coefficient biases, we thus compare them on their ability to improve $Y$
predictions of out-of-sample data when one factor is introduced into the model.
This analysis leads to a $\Delta R$ as described in Algorithm
\ref{algorithm:b2b_fi}). As expected, the Forward, CCA, PLS
and B2B method predicted that the Dummy Variable does not improve the $Y$
prediction. This confirms that these methods accurately rule out the known
non-causal factor.

### 2020-05-20 paper/paper.tex
up

  \node[] (sim1) at (0,-3.25) {\scalebox{0.85}{$X \sim P(X)$}};
  \node[] (sim2) at (0,-3.65) {\scalebox{0.85}{$N \sim P(N)$}};
  \node[] (reg1) at (6,-3.25) {$\hat{S} = \text{diag}(\underbrace{(X_2^\top X_2 + \Lambda_X)^{-1} X_2^\top Y_2\overbrace{(Y_1^\top Y_1 + \Lambda_Y)^{-1} Y_1^\top X_1}^{\text{1) } \hat{X} : \text{ regression from } Y \text{ to } X}}_{\text{2) regression from } X \text{ to } \hat{X}})$};
  \end{tikzpicture}
  \caption{Back-to-back regression identifies the subset of factors $S_{ii} = 1$ in $X$ that influence some observations $Y$ by 1) regressing from $Y$ to $X$ to obtain $\hat{X}$, and 2) returning the diagonal of the regression coefficients from $X$ to $\hat{X}$.}
\label{fig:b2b}
\end{figure}

@@

We consider the measurement of multivariate signal $Y \in \mathbb{R}^{m \times
d_y}$ (the dependent variables), generated from a set of putative causes $X \in \mathbb{R}^{m \times
d_x}$ (the independent variables), via some unknown linear apparatus $F \in \mathbb{R}^{d_x \times d_y}$.
%
Not all the variables in $X$ exert a causal influence on $Y$.
%
By considering a square binary diagonal matrix of \emph{causal influences} $S
\in \mathbb{D}^{d_x \times d_x}$, we denote by $XS$ the causal factors of $Y$.
%
In summary, the problem can be formalized as:
%
\begin{equation}
    y_i = (x_i S + n_i) F
    \label{eq:model}
\end{equation}
%
where $i$ is a given sample, and $n_i$ is a sample-specific additive noise drawn from a
centered distribution.
%
While the triplet of variables $X$ and $N$ are independent, we allow each of
them to have any form of covariance.
% what is a general covariance matrix?
%
In practice, we observe $m$ samples $(X, Y)$ from the model.
%
This problem space, along with the sizes of all variables involved, is
illustrated in Figure~\ref{fig:b2b}.
%
Given the model in Equation~\cref{eq:model}, the goal of Back-to-Back
Regression (B2B) is to estimate the matrix $S$, i.e. to identify the factors
that most reliably account for the multivariate observations.

@@

%
% After obtaining $\hat{S}$, we can fit a final regression from $X \hat{S}$ to $Y$.

@@

@@

\section{Related work}

% Forward and cross-decomposition models have been used to identify the causal
% contribution of correlated factors onto multi-dimensional observations (e.g.
% \citep{naselaris2011encoding}). These approaches typically lead to multiple
% coefficients for each features (i.e. one per dimension of $Y$ or one per
% component respectively). Furthermore, these coefficients can be difficult to
% summarize into a single causal estimate. By contrast, B2B quickly (Fig.
% \ref{fig:duration}) leads to a single unbiased scalar values $\hat S$ tending
% towards 1 and 0 for causal and non-causal features respectively.

A variety of statistical methods applied to neuroimaging have been
proposed to clarify what is being represented in brain responses - i.e. what
feature causes specific brain activity. For example, CCA and PLS have been used in
neuroimaging for a variety of purposes such as
denoising and subject alignment \citep{cca_hotelling, de2019multiway}. While CCA
and PLS relates to B2B, these methods diverge in several ways. First, they have different objectives: CCA aims to find the potentially numerous and poorly
interpretable components where $X$ and $Y$ are maximally correlated, whereas B2B
aims to recover the causal factors from X to Y. Second, B2B is not symmetric
between $X$ and $Y$: it aims to identify specific causal features by first
optimizing over the decoders $G$ and then over $H$. By contrast, CCA and PLS are
symmetric between $X$ and $Y$, and aims to find $G$ and $H$ such that they
project $X$ and $Y$ on maximally correlated dimensions. Third, CCA is based an
eigen decomposition of $XH$ and $YG$ - the corresponding canonical components
are thus mixing the $X$ features in way that limit interpretability and
potentially dilute the impact of each feature onto multiple components. In
contrast B2B assesses each feature $X^j$ on a single $Y$ component specifically
selected to maximize signal-to-noise ratio of that feature $j$. Fourth CCA does
not separately optimize two distinct regularization
parameters for $G$ and $H$, where B2B does. Finally, CCA does not use different data splits to
estimate $G$ and $H$. Together, these differences may explain why B2B reliably
outperform CCA on estimating causal influences (Figs. \ref{fig:percondition} and
\ref{fig:auc_plots}).

One popular multivariate analysis of brain activity is
Representational Similarity Analysis (RSA)
\citep{kriegeskorte2008representational}, and consists in analyzing the
similarity of brain responses associated with specific categorical conditions
(e.g. distinct images), by (1) fitting one-against-all classifiers on each
condition and (2) testing whether these classifiers can discriminate all other
conditions. The resulting confusion matrix is then analyzed, generally in an unsupervised
manner, to reveal which conditions lead to similar brain activity patterns. B2B
differs from RSA in that it uses regressions instead of one-hot classifications.
Consequently, and unlike RSA, B2B (1) is fully supervised (2) provides
interpretable coefficients and (3) can generalize to new items and new contexts.
In practice, these elements allow B2B to apply to event-related paradigms and
latent variable analyses.

The present empirical results, together with their theoretical foundations,
suggest that B2B may come as a tool of choice for causal discovery when
feature-wise intervention is limited.

\section{Acknowledgements}
We are thankful to Gael Varoquaux and Alexandre Gramfort for the valuable
feedback. This work was supported by ANR-17-EURE-0017 and the Fyssen Foundation
to JRK.

>>>>

  \node[] (sim1) at (0,-3.25) {\scalebox{0.85}{$X \sim P(X)$}};
  \node[] (sim2) at (0,-3.65) {\scalebox{0.85}{$N \sim P(N)$}};
  \node[] (reg1) at (6,-3.25) {$\hat{S} = \text{diag}(\underbrace{(X_2^\top X_2 + \Lambda_X)^{-1} X_2^\top Y_2\overbrace{(Y_1^\top Y_1 + \Lambda_Y)^{-1} Y_1^\top X_1}^{\text{1) } \hat{X} : \text{ regression from } Y \text{ to } X}}_{\text{2) regression from } X \text{ to } \hat{X}})$};
  \end{tikzpicture}
  \caption{Back-to-back regression identifies the subset of factors $S_{ii} = 1$ in $X$ that influence $m$ multidimensional observations $Y$ by 1) regressing from $Y$ to $X$ to obtain $\hat{X}$, and 2) returning the diagonal of the regression coefficients from $X$ to $\hat{X}$.}
\label{fig:b2b}
\end{figure}

@@

We consider the measurement of multivariate signal $Y \in \mathbb{R}^{m \times
d_y}$ (the dependent variables), generated from a set of putative causes $X \in \mathbb{R}^{m \times
d_x}$ (the independent variables), via some unknown linear apparatus $F \in \mathbb{R}^{d_x \times d_y}$.
%
Not all the variables in $X$ exert a causal influence on $Y$.
%
By considering a square binary diagonal matrix of \emph{causal influences} $S
\in \mathbb{D}^{d_x \times d_x}$, we denote by $XS$ the causal factors of $Y$.
%
In summary, the problem can be formalized as:
%
\begin{equation}
    y_i = (x_i S + n_i) F
    \label{eq:model}
\end{equation}
%
where $i$ is a given sample, and $n_i$ is a sample-specific additive noise drawn from a
centered distribution.
%
While $X$ and $N$ are independent, we allow each of
them to have any form of covariance.
% what is a general covariance matrix?
%
In practice, we observe $m$ samples $(X, Y)$ from the model.
%
This problem space, along with the sizes of all variables involved, is
illustrated in Figure~\ref{fig:b2b}.
%
Given the model in Equation~\cref{eq:model}, the goal of Back-to-Back
Regression (B2B) is to estimate the matrix $S$, i.e. to identify the factors
that most reliably account for the multivariate observations.

@@

@@

Note that $\S hat$ is unbiased, in the sense that it is centered around zero when there is no
effect, only if the second regression $H$ is not regularized. Second-level
statistics testing whether $\S hat$ is superior to 0 are thus only valid if $H$
is not regularized.

@@

\section{Discussion}

Here, we introduce B2B, a method to disentangle the causal contribution of
collinear factors from multidimensional observations. After proving the validity
of B2B, we show that it compares favorably against baseline models, such as
Backward, Forward, CCA and PLS models both on a wide spectrum of synthetic data,
and on two large neuroimaging datasets.

In addition, B2B can be very fast to compute as long as both $H$ and $G$ are based
on l2 optimization with l2 regularization \ref{fig:duration}. Furthermore, B2B
need not be limited to these standard optimizations: the $H$ and $G$ operators
can in principle be found with e.g. support vector or random forest regression.
We reserve the study of these computational variants to future work.

Like Forward and cross-decomposition models, B2B is limited by the correlations
between factors. At the extreme, if two factors are identical, and thus fully
correlated, none of these statistical method can disentangle the causal
contribution of each of them separately. In practice, this implies that, like
general linear models, B2B will best work with high signal-to-noise ratio and/or
orthogonal factors, and will see its sensitivity diminish when the
signal-to-noise ratio of collinear factors drops.

In the present neuroimaging context, B2B follows a long series of statistical
methods designed to characterize brain representations - i.e. to identify what
sensory feature causes specific brain responses \citep{naselaris2011encoding}.
In this regard, CCA and PLS have been used in electrophysiology and neuroimaging
for tracking representations (e.g. \citep{musch2020transformation}) as well as
for denoising and subject alignment \citep{cca_hotelling, de2019multiway}. While
CCA and PLS relates to B2B, these methods diverge in several important ways.
First, they have different objectives: CCA aims to find the potentially numerous and poorly
interpretable components where $X$ and $Y$ are maximally correlated, whereas B2B
aims to recover the causal factors from X to Y. Second, B2B is not symmetric
between $X$ and $Y$: it aims to identify specific causal features by first
optimizing over the decoders $G$ and then over $H$. By contrast, CCA and PLS are
symmetric between $X$ and $Y$, and aims to find $G$ and $H$ such that they
project $X$ and $Y$ on maximally correlated dimensions. Third, CCA is based an
eigen decomposition of $XH$ and $YG$ - the corresponding canonical components
are thus mixing the $X$ features in way that limit interpretability and
potentially dilute the impact of each feature onto multiple components. In
contrast B2B assesses each feature $X^j$ on a single $Y$ component specifically
selected to maximize signal-to-noise ratio of that feature $j$. Fourth CCA does
not separately optimize two distinct regularization parameters for $G$ and $H$,
whereas B2B does. Finally, CCA does not use different data splits to
estimate $G$ and $H$. Together, these differences may explain why B2B reliably
outperform CCA on estimating causal influences (Figs. \ref{fig:percondition} and
\ref{fig:auc_plots}).

One popular method to investigate multidimensional patterns of brain activity is
Representational Similarity Analysis (RSA)
\citep{kriegeskorte2008representational}. RSA quantifies the
similarity of brain responses associated with specific categorical conditions
(e.g. distinct images), by (1) fitting one-against-all classifiers on each
category and (2) testing whether these classifiers discriminates all other
categories. The resulting categories $\times$ categories confusion matrix is
then analyzed, generally in an unsupervised manner, to reveal the categories
that present similar brain activity patterns. B2B
subsumes RSA in that (1) it uses regressions instead of one-hot
classifications and (2) it is fully supervised.
Consequently, and unlike RSA, B2B (1) provides interpretable coefficients and
(2) can generalize to new items and new contexts. In practice, these elements
allow B2B to apply to event-related paradigms and latent variable analyses,
whereas RSA can only be applied when the same one-hot-encoded condition is
repeated multiple times.

More generally, the present empirical results, together with their theoretical
foundations, suggest that B2B may serve as a method of choice for causal
discovery when feature-wise intervention is limited.

\section{Acknowledgements}
We are thankful to Gael Varoquaux and Alexandre Gramfort for the valuable
feedback. This work was supported by ANR-17-EURE-0017 and the Fyssen Foundation
to JRK for his work at PSL.
